%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[margin, 10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above

\setlength{\textwidth}{5.1in} % Text width of the document

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\large\bf Jhonatan Ismael Castro Rocabado} % Your name at the top
 
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'
 
\moveleft.5\hoffset\centerline{jhtan@jhtan.com}
\moveleft.5\hoffset\centerline{(591) 73278380}

%----------------------------------------------------------------------------------------

\begin{resume}

%Additionally, for US positions, do not include age, marital status, or nationality.This sort of personal information is not appreciated by companies, as it creates a legal liability for them. (Cracking the Coding Interview, pg 38)

%\section{Nationality}
%Bolivian.

%\section{Date of Birth}
%March 25 of 1991.

\section{Education}
\begin{itemize}
\item[] Currently enrolled at the fourth year of "Licenciatura en Inform\'atica" at "Universidad Mayor de San Andr\'es".
\end{itemize}

\section{Technical Skills}
\begin{itemize}
\item[] {\sl Programming Languages:} \\
Prefered: C++(proficient), JavaScript(proficient), PHP(proficient), Python(prior experience), Ruby(prior experience). \\
Other: Java, C, CSS, HTML, LaTeX, Emacs Lisp. \\
\item[] {\sl Other experience} \\
Linux, Git, Emacs, Apache, Nginx, jQuery, Angular, Laravel, Rails, Django, Agile Development, Drupal.
\end{itemize}
 
\section{Working Experience}
\begin{itemize}
\item[] {\sl Intern Developer} \\
at Nemetec since august 2010 to january 2011. Working on Java web services for the Bisa bank. \\
\item[] {\sl Teacher Assistant} \\
at ``Universidad Mayor de San Andr\'es" in the subject of ``Introduction to Programming'' since 2011 to 2012. \\
\item[] {\sl Software Developer} \\
  at Coderoad since march 2012 to december 2013. Working on the project www.incollect.com \\
 \item[] {\sl Teacher Assistant} \\
   at ``Universidad Mayor de San Andr\'es" in the subject of ``Introduction to Programming'' 2016. \\
   \item[] {\sl Software Enginieer} \\
  at Coderoad since september 2016 to now.\\
\end{itemize}

\section{Personal Blog}
\begin{itemize}
\item[] www.jhtan.com
\end{itemize}

\section{Github Page}
\begin{itemize}
\item[] www.github.com/jhtan
\end{itemize}

\section{Courses}
\begin{itemize}
\item[] {\sl 2013}, ``Maratona de Programa\c{c}\~ao'' at ``Universidade Campinas'' in Campinas Brazil. \\
\item[] {\sl 2014}, ``Campamento de Programaci\'on'' at ``Universidad San Pablo'' in Arequipa Per\'u.\\
\item[] {\sl 2014}, ``Training Camp Argentina'' at ``Universidad de Buenos Aires'' in Buenos Aires Argentina.
\end{itemize}

\section{Achievements and Competitions}
\begin{itemize}
\item[] {\sl 2009, 2010, 1012} \\
Honorable mention at Latin American ACM-ICPC progamming contest in the bolivian sub region. \\
\item[] {\sl 2011} \\
Third place at Latin American ACM-ICPC progamming contest in the bolivian sub region. \\
\item[] {\sl 2014} \\
Global Game Jam, bolivian site. First place. \\

\item[] {\sl 2014} \\
  Sixth place at Latin American ACM-ICPC progamming contest in the bolivian sub region. \\

\item[] {\sl 2013, 2014, 1015} \\
  Coach of some teams from my university at Latin American ACM-ICPC progamming contest, winning the first place at bolivian sub region on 2015. \\
  
\item[] {\sl Topcoder} \\
Maximum raiting of 1247 points (blue coder). \\
\item[] {\sl Codeforces} \\
Maximum raiting of 1675 points (blue coder). \\
\end{itemize}

\section{Extracurriculars}
\begin{itemize}
\item[] Founder of the first Hacker Space in Bolivia. www.hacklab.org.bo \\
\item[] Founder of the ``Hackmeeting Bolivia'' event. www.hackmeeting.org.bo \\
\item[] {\sl 2013, 2014, 2015}, teacher at ``Olimpiada Boliviana de Inform\'atica'' training camps. \\
\item[] Coach of La Paz's team in ``Olimpiada Boliviana de Inform\'atica'' (2014, 2015)\\
\end{itemize}


\end{resume}
\end{document}
